Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-08-16 Docs/Paper/LaTex/template.tex
Conclusions Fixed

Finally, there is an issue about 150 nodes problem, since it seems to be the limit of ESBMC. It really depends on the modeling granularity of the problem. Some researchers propose fine-grained models, in which each instruction can be mapped to either HW or SW. This may lead to thousands of nodes or even more. Others defend coarse-grained models, where decisions are made for bigger components, thus even complex systems may consist of just some dozens of nodes to partition. In principle, a fine-grained approach may allow to obtain better partitions, but at the cost of an exponential increase of the size of the search space. In future work, we will exploit other search strategies in the multi-core ESBMC approach and address specifically more complex types of architectures in the HW-SW partitioning problem, including more than one CPU.
\section{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%
% ---- Bibliography ---- %
%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Finally, there is an issue about 150 nodes problem, since it seems to be the limit of ESBMC. It really depends on the modeling granularity of the problem. Some researchers propose fine-grained models, in which each instruction can be mapped to either HW or SW. This may lead to thousands of nodes or even more. Others defend coarse-grained models, where decisions are made for bigger components, thus even complex systems may consist of just some dozens of nodes to partition. In principle, a fine-grained approach may allow to obtain better partitions, but at the cost of an exponential increase of the size of the search space. \textcolor{Red}{Em trabalhos futuros, vamos abordar melhorias na abordagem do ESBMC, esperamos eliminar a camada de paralelismo da arquitetura do ESBMC implementando open MP diretamente em seu nucleo, almejamos assim otimizar o tempo de processamento.}
\section{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%
% ---- Bibliography ---- %
%%%%%%%%%%%%%%%%%%%%%%%%%%
